---
title: "Colab on Data science : Tips on starting to use R"
author: "Doris Suzuki Esmerio"
date: '2023-05-31'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# How to import data into R ? ----

1) For beginners : Click on "import dataset".
2) For making a reproducible script: follow the instructions below.

### Set up the right directory ----

Simple set up :
1) New project
2) Crete New for creating a new folder. Or Use Existing Directory if you already have a folder on your local computer. 
3) Create a folder to include your datasets. 


If you want to include version control (it is a best practice):
1) Set up a Github repository
2) Open RStudio, Click on "Create New Project" , Version control , then paste the url from you github repository
3) You can create a folder to include your datasets, either by the folder directory, or by code :

```{r}
dir.create("Data")
```


#### Check ----

```{r}
getwd() # this should show you where you are
```


# Load data

```{r, eval=FALSE}

### Load libraries ----

library(readxl) # for xlsx
library(readr) # for csv

# Load data ----
df <- read_xlsx("Data/example.xlsx",
				sheet = 1)

dataset <- read_csv("Data/example.csv")
```



# How to look at the data:

```{r, eval=FALSE}
df %>% glimpse()

df %>% View()


```


# Keyboard shortcuts ----

Run line of code: cntrl + enter

Save file : cntrl + s

Pipe ( %>% ): cntrl + shift + m

Comment line : cntrl + shift + c


